The past and future of visualization for computing in science and engineering

### 2020-03-28 CombaWeiskopf2020/paper.tex
remove redundancy

\IEEEtitleabstractindextext{%
\begin{abstract}
A retrospective of the CiSE Visualization Corner (VizCorner) department since 2011 leads us to identify current and future developments in visualization research and their impact on computing in science and engineering.
The VizCorner  reflects the long-term and fruitful overlap between computer-based visualization and computational science and engineering. 
Looking into what we have covered in VizCorner for the last decade, we connect with current trends in visualization research, leading to possible future developments for visualization in science and engineering.
\end{abstract}
}

@@

The CiSE Visualization Corner (VizCorner) department covers the breadth of visualization research and practice relevant to the readers of this magazine. We provide a glimpse of basic research questions and highlight the practical impact of visualization.
As early as 1987, the Workshop on Visualization in Scientific Computing identified the need for visualization for the growing area of simulation-oriented science~\cite{NSFreport1987}. Visualization now plays a key role in visual data analysis and communication in science, engineering, and beyond. 
Organizing the papers from 2011 until now into themes highlights the focal areas of the VizCorner, 
and illustrates the breadth of visualization possibilities.

>>>>

\IEEEtitleabstractindextext{%
\begin{abstract}
The CiSE Visualization Corner (VizCorner) department  reflects the long-term and fruitful overlap between computer-based visualization and computational science and engineering. 
Looking into what the VizCorner has covered in the last decade, we identify current trends in visualization research,  and possible future developments for visualization in science and engineering.
\end{abstract}
}

@@

The CiSE Visualization Corner (VizCorner) department covers the breadth of visualization research and practice relevant to the readers of this magazine. 
As early as 1987, the Workshop on Visualization in Scientific Computing identified the need for visualization for the growing area of simulation-oriented science~\cite{NSFreport1987}. Visualization now plays a key role in visual data analysis and communication in science, engineering, and beyond. 
Organizing the papers from 2011 until now into themes highlights the focal areas of the VizCorner, 
and illustrates the breadth of visualization possibilities.
